---
title: "Week 10 Presentation"
author: "Yen-Ting Chen"
date: "2020/11/30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading `iris`

Load `iris` and filter out all the other two species expect setosa.
```{r}
# Week 10 pres.
rm(list = ls())
data(iris) # measurement in centimeters
library(dplyr)
se <- iris %>% filter(Species == "setosa")
```

### Simple linear regression

Let's say that I am interested in the relationship between sepal length and other factors.

I first run `lm` on setosa's sepal length and width and see how it goes.

```{r}
# lm btw sepal length and width
model1<- lm(Sepal.Length~Sepal.Width, se) # checking the relationship betwenn sepal width and length
summary(model1)
```
Small p value from F statistics and strong significance of sepal width and the intercept. It is clear that there is a strong numerical relationship betweeen sepal length and width.

A graphical illustration
```{r}
# graphical illustration
library(ggplot2)
ggplot(se) + aes(x = Sepal.Width, y = Sepal.Length) + geom_point() + # structure of ggplot
  labs(title = "setosa", x = "Sepal Width (cm)", y = "Sepal Length (cm)") + # title, xlab, ylab 
  stat_smooth(method = "lm", ) # reg line
```

### Multiple linear regression

Now I am curious about how other factors interact with sepal length in the species setosa (numerically of course!).

I run `lm` on all the other factors regarding setosa.

```{r}
# checking all the variables within setosa
model2 <- lm(Sepal.Length~., se[,1:4])
summary(model2)

```
What we see right here is significance in r statistics, yet only sepal width  and the associated intercept shows significance.

Checking the prediction power between model1 and model2.
```{r}
sigma(model1)/mean(iris$Sepal.Length)
sigma(model2)/mean(iris$Sepal.Length)
```
Model2 is slightly better than model1 (by 0.03%).

### Model selection

Now considering finding/selecting the best model.

```{r}
MASS::stepAIC(model2)
fore <- MASS::stepAIC(model2, direction = "forward")
back <- MASS::stepAIC(model2, direction = "backward")
```

The result of AIC told us that the more variables we include in the model, the higher the accuracy. 

However, with the 0.03% residual error difference, I don't think the hard work of including more variables is worth the trouble.
