---
title: "Week 4 pres."
author: "R08241220  Chen, Yen Ting"
date: "2020/10/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Plotting Practice**
  
## Data
  Three time series giving the monthly deaths from bronchitis, emphysema and asthma in the UK, 1974–1979, both sexes (ldeaths), males (mdeaths) and females (fdeaths).

```{r, echo=T}
rm(list = ls())
da <- ldeaths # A time series data of monthly deaths from lung diseases in UK from 1974 to 1979; contains both sexes
md <- mdeaths # male deaths
fd <- fdeaths # female deaths
```

### Comparison between sexs and overall deaths.
Plotting out the deaths of males, females, and the two combined throughout 1974-1979.

```{r, echo=T}
# Total deaths, male deaths, female deaths####
# blank plot
plot(da,
     main = "Monthly Deaths From Lung Diseases in UK (1974-1979)",
     xlab = "Year",
     ylab = "Death Count",
     ylim = range(da,md,fd),
     type = "n")
# adding lines
lines(da, col = "Purple", lwd = 3) #total deaths
lines(md, col = "Blue", lwd = 3) # male deaths
lines(fd, col = "Red", lwd = 3) # female deaths
legend(x = "topright", legend = c("Total Deaths", "Male Deaths", "Female Deaths"),
       col = c("Purple", "Blue", "Red"),
       lwd = 3)
#dev.off()
```
1. Periodocity in all datasets.

2. The death of males is significantly larger than that of females.

### Comparison between years

Let's examine the dataset first.
```{r, echo = T}
# examine the data
ldeaths
class(ldeaths)
```

A matrix-like structure wwould appear, yet it is not a matrix nor a data frame, it is a time series data. Therefore, there is need to modify the three datasets. 

To reshape the data sets:

`time()` extracts time from a time series data; returns years with decimals.

`floor()` runs a filter; turning all numbers into integers

`unique()` filters out repeated elements.


```{r, echo=T}
time(da)
floor(time(da))
unique(floor(time(da))) # extracting years
```
Regarding months, abbreviations of months already stored in R. 

```{r, echo=T}
# regarding months
month.abb # returns abbreviated month names
month.name # returns complete month names
# these two are very useful. Gotta remember this lol

time <- list(month.abb, unique(floor(time(da))))
# a series of function to store time data into a list (so matrix()'s dimnames can load them)
```

Since the time range of the three datasets are identical, there should be no problem for using the same object in the `dimnames` argument.
```{r, echo=T}
# merges time data and no. of deaths back together
# creates a new data frame 
nd <- as.data.frame((matrix(da, 12, dimnames = time)))
nmd <- as.data.frame((matrix(md, 12, dimnames = time)))
nfd <- as.data.frame((matrix(fd, 12, dimnames = time)))
```

Now plotting with the reshaped datasets.
```{r, echo=T}
#
par(mfrow = c(2,2))

# total
plot(nd[,1], # blank plot
     main = "(a) Total Deaths Between Years",
     type = "n",
     ylab = "No. of Deaths",
     xlab = "Months",
     ylim = range(nd))
for (i in 1:ncol(nd)) { # for loop for drawing all the years
  lines(nd[,i], col = i, lwd = 3)
}

legend(x = "topright", legend = colnames(nd), # legend
       col = 1:ncol(nd), lwd = 3, cex = 0.5)

# Male
plot(nmd[,1], # blank plot
     main = "(b) Male Deaths Between Years",
     type = "n",
     ylab = "No. of Deaths",
     xlab = "Months",
     ylim = range(nmd))
for (i in 1:ncol(nmd)) { # for loop for drawing all the years
  lines(nmd[,i], col = i, lwd = 3, lty = 3)
}
legend(x = "topright", legend = colnames(nmd), # legend
       col = 1:ncol(nmd), lwd = 3, lty = 3, cex = 0.5)

# Female
plot(nfd[,1], # blank plot
     main = "(c) Female Deaths Between Years",
     type = "n",
     ylab = "No. of Deaths",
     xlab = "Months",
     ylim = range(nfd))

for (i in 1:ncol(nfd)) { # for loop for drawing all the years
  lines(nfd[,i], col = i, lwd = 3, lty = 4)
}  
legend(x = "topright", legend = colnames(nfd), # legend
       col = 1:ncol(nfd), lwd = 3, lty = 4, cex = 0.5)

# total + male + female
plot(nfd[,1], # blank plot
     main = "(d) Comparison Among Datasets",
     type = "n",
     ylab = "No. of Deaths",
     xlab = "Months",
     ylim = range(nd, nfd))
for (i in 1:ncol(nd)) { # for loop for drawing all the years
  lines(nd[,i], col = 1, lwd = 3)
}
for (i in 1:ncol(nmd)) { # for loop for drawing all the years
  lines(nmd[,i], col = 2, lwd = 3, lty = 3)
}
for (i in 1:ncol(nfd)) { # for loop for drawing all the years
  lines(nfd[,i], col = 3, lwd = 3, lty = 4)
}  
legend(x = "topright", legend = c("Total Deaths", "Male Deaths", "Female Deaths"), # legend
       col = 1:3, lwd = 3, lty = c(1,3,4), cex = 0.5)
#title(main = "Comparison Between Years")
par(cex.main = 0.1)
```
1. The curvature looks identical within years and within sexes.

2. Maximum deaths occur at winter; minimum deaths occur at summer.
