---
title: "Week6 Pres."
author: "R08241220  Chen, Yen Ting"
date: "2020/10/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro
I decide to plot the bathymetric map for my thesis.
The topic of my thesis is the comparison of benthic communities of the Gaoping River and Pearl River continental shelf. 

My strategy is simple: First, I plot out the bathymetric map with the introduced package -- `marmap`. After that, I add the coordinates and the names of the respective stations with the in-built functions of R (`graphics`).

## 1. Bathymetric map
Downloading data from NOAA
```{r}
rm(list = ls())
library(marmap)
ba <- getNOAA.bathy(lon1=111,lon2=124, lat1=20,lat2=26,resolution=1)
```

Creating a function of color palette for water depth color-coding.
```{r}
# generate a color gradient function for plot.bathy
oc <- colorRampPalette(c('cyan', 'darkblue', "purple"))
oc # returns a function; type in numbers and then the function will do its work
te <- colorRampPalette(c("lightgreen", "darkgreen"))
```

Plotting it out.

a. `deepest.isobath`, `shallowest.isobath` & `step` need to be work in tandem (which performs like a matrix).
b. `bpal` inputs the color palette function with the depth. It works like this: list(c(depth range (`two integers; small to large`), `the color function`)
```{r, fig.keep='all'}
fi <- plot.bathy(ba, # data
           image = T, # color the depth layers
           deepest.isobath = c(-6000, -300, -100, 0), # deepest isobath
           shallowest.isobath = c(-1000, -100, 0, 0), # shallowest isobath
           step = c(2000, 100, 20, 0), # distance btw two isobaths
           lwd = c(0.5, 1, 1, 2), # isobath line width
           lty = c(1,1,1,1), # isobath line type
           col = c("grey", "black", "black", "black"),
           drawlabels = c(T,T,T,F), #whether plot the depth on the isobaths
           land = T,
           bpal = list(c(0, max(ba), te(100)),c(min(ba), 0, rev(oc(100)))) ) # a list of depth bounds and colors
text(x = 121, y = 24, "Taiwan", cex = 1.2)
text(x = 116, y = 25, "China", cex = 1.2)
# input sample sites
library(readxl)
da <- read_xlsx("C:\\Users\\tumha\\Desktop\\Lab Work\\Field work\\LGD2006\\OR1_1242_LGD_2006_Station.xlsx",col_names = T)
ss <- data.frame(da$Station, da$Longitude, da$Latitude)
points(x = da$Longitude, y = da$Latitude, pch = 18, col = 2, cex = 2)
text(x = da$Longitude, y = da$Latitude+0.5, da$Station, col = 2, cex = 0.8, font = 2)
```

