---
title: "Week 2 pres."
author: "R08241220  Chen, Yen Ting"
date: "2020/9/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Sec. 1 Column extraction

Did you know that you can extract columns by their names?
Try type down the desired column name within quotation marks and brackets.
```{r}
iriss <- iris[sample(nrow(iris), 15),]
iriss$Species    # method 1
iriss[,5]        # method 2 
iriss["Species"] # method 3
```
Yet something intersting occurs: method 3 does not return a character vector like the previous two; method 3 returns a part of the data frame.

```{r}
class(iris["Species"])
```
```{r}
iris[c("Species", "Sepal.Width")]
iris[Species,] # you need to quotate the column name, or as a default, R will recognize it as a object in the global environment.
```



So what are the implications?
TBH, I'm not sure.


## Sec. 2: Challenge

Load the data and add a new column called pot.serial.number for the sake of identification.

```{r, echo = T}
rm(list = ls())
# load
ra <- read.table('https://raw.githubusercontent.com/vianneydenis/attentive-suricate/master/Data/rairuoho.txt', sep = "\t", header = T)
# Reformat the table in order to have the day as a variable with 6 levels together with another variable called length. 
ra$pot.serial.number <- 1:nrow(ra) # generates a new column for identification
head(ra)
```


Now Im loading tidyr function for reshaping the data into a long format.

```{r, echo = T}
library(tidyr)
rera <- ra %>% gather("day", "length", "day3", "day4", "day5", "day6", "day7", "day8")
head(rera)
```

