---
title: "Week 3 Pres."
author: "R08241220  Chen, Yen Ting"
date: "2020/10/6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  **RP5**
  Create the following data frame summarizing the results of a small experiment on 5 individuals testing the efficiency of a specific diet (drinking bubble tea only - feak data). 

```{r, echo=TRUE}
rm(list = ls())
before_diet <- c(104, 95, 87, 77, 112)
after_diet <- c(96, 91, 81, 75, 118)
individuals <- c("subject_1", "subject_2", 'subject_3', "subject_4", 'subject_5')
da <- data.frame(before_diet, after_diet, row.names = individuals)
da
```

  Create another vector with the weight loss (in %) associated with subject no.

```{r,echo=TRUE}
da$weight_loss <-
  (((after_diet-before_diet)/before_diet)*100)
(after_diet-before_diet)/before_diet*100
100-(after_diet/before_diet*100)

da
```

What can you say on this bubble tea diet? 
```{r}
da
summary(da)
```
The result suggests the bubble tea diet has a mean weight loss of 3.2 %. However, the varying results of bubble tea diet among individuals indicates that other factors might have their influences.

---
  Reformat the table by creating: a variable individual with the identity of the five individuals, a variable diet with two levels before and after, a variable weight containing the weight before and after the diet.


```{r,echo=TRUE}
library(tidyr)
da$individual <- row.names(da) # extracts rownames and input them as a new variable
nd1 <- da %>%  # long data
  pivot_longer(before_diet:after_diet, names_to = "diet" ,values_to = "weight")
nd1$diet <- as.factor(nd1$diet) # factorize "diet"
nd1 # final result
```

