---
title: "Week 2 pres."
author: "R08241220  Chen, Yen Ting"
date: "2020/9/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## **Reveiw: Data manipulation**
I am going to take everyone to review some data extraction techniques.

# Sec. 1 Matrix notation
The following method uses a matrix-notation style -- object[# of rows, # of columns].

```{r}
a <- iris[sample(nrow(iris), 15),]
a[1,]
```


```{r}
a[,2]
```

```{r}
a[1,2]
```

If there is no input of comma within the brackets, R reads it as a column by default.

```{r}
a[1]
```

Furthermore, adding a subtraction mark in front of the numbers removes the row/column.

```{r}
a[-1]
```

Here, a question emerges -- what pattern would be displayed if we put minus signs within the brackets?  
```{r}
a[1,2] #returns a single value 
a[-1,2] # removes the first row and returned the second column.
a[1,-2] # likewise, this line removes the second column and returned the first row.
a[-1,-2] # This removes the first row and the second column of iris
```
The key takeaway here (at least that's what I thought) is that you cannot remove a single value by inputting minus signs in front of the indicators of rows and columns.

What if you have the need to change up one number within the data frame?

You can try this:
```{r}
b <- iris # setting up a data frame
b[1,1] # returns 5.1
b[1,1] <- 6.1 # inputting 6.1 into a[1,1]
b[1,1]
```

## Something interesting: Column extraction
Did you know that you can extract columns by their names?

Try type down the desired column name within quotation marks and brackets.

```{r}
iriss <- iris[sample(nrow(iris), 15),]
iriss$Species    # method 1
iriss[,5]        # method 2 
iriss["Species"] # method 3
```
Yet something interesting occurs: method 3 does not return a character vector like the previous two; method 3 returns a part of the data frame.

```{r, echo=T}
class(iriss["Species"])
iriss[c("Species", "Sepal.Width")]
#iriss[Species,] 
# you need to quotate the column name, or as a default, R will recognize it as a object in the global environment.
```

So what are the implications?
TBH, I'm not sure. Hope you guys can find that interesting. :)


## Sec. 2: Challenge

Load the data and add a new column called pot.serial.number for the sake of identification.

```{r, echo = T}
rm(list = ls())
# load
ra <- read.table('https://raw.githubusercontent.com/vianneydenis/attentive-suricate/master/Data/rairuoho.txt', sep = "\t", header = T)
# Reformat the table in order to have the day as a variable with 6 levels together with another variable called length. 
ra$pot.serial.number <- 1:nrow(ra) # generates a new column for identification
head(ra)
```


Now Im loading tidyr function for reshaping the data into a long format.

```{r, echo = T}
library(tidyr)
rera <- ra %>% gather("day", "length", "day3", "day4", "day5", "day6", "day7", "day8")
head(rera)
```

